% Based on Sourabh Bajaj's resume template at https://github.com/sb2nov/resume

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{enumitem}
\usepackage{nopageno} % remove page numbers

% Reformat the section headers
\titleformat{\section}
{\scshape\Large}
{}
{0em}
{}[\titlerule]

% Reformat the title
\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries\theauthor}

\vspace{0.5em}

samarthkishor1@gmail.com $\cdot$ github.com/samarthkishor

\end{center}}

% Handle the Work Experience and Projects subheadings
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2em}}

\newcommand{\workSubheading}[5]{
\setlength\itemsep{-0.25em}
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\large#1} & {\small #2} \\
\textit{#3} & {#4}
\end{tabular*}
\vspace{-1.25em}
\begin{itemize}
\item #5
\end{itemize}}

% Handle the Education subheadings
\newcommand{\eduSubheading}[4]{
\item
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\large#1} & {\small #2} \\
\textit{#3} & {#4}
\end{tabular*}}

% Handle the Skills entries
\newlength{\spacebox}
\settowidth{\spacebox}{Programming Languages}

\newcommand{\skillEntry}[2]{
\setlength\itemsep{0.25em}
\item
\hspace{1em}\parbox{\spacebox}{
\raggedright{\textbf{#1}}}
\hspace{-2.5em} #2 \par}


% Begin Resume
\begin{document}

\title{R\'esum\'e}
\author{Samarth Kishor}

\maketitle
\vspace{-3em}
%-----------------------------------------------

\section{Education}

\resumeSubHeadingListStart{}

\eduSubheading{University of Virginia}{Charlottesville, VA}
{BA Computer Science, Technology Entrepreneurship Minor}{Expected Graduation: 2021}
\vspace{-1.25em}
\begin{itemize}
\item \textbf{Cumulative GPA:} 3.67
\item \textbf{Relevant Coursework:} Software Development Methods\ \ $\cdotp$\ \ Program and Data Representation\ \ $\cdotp$\ \ Algorithms\ \ $\cdotp$\ \ Theory of Computation
\end{itemize}

% \eduSubheading{Maggie L. Walker Governor's School}{Richmond, VA}
% {Advanced Studies Diploma}{2013--2017}
% \vspace{-1em}
% \begin{itemize}
% \item Completed 142 hours of community service.
% \item Cross Country and Outdoor Track athlete.
% \item NHS\ \ $\cdotp$\ \ Mu Alpha Theta\ \ $\cdotp$\ \ Sociedad Honoraria Hisp\'anica\ \ $\cdotp$\ \ Japanese Honor Society
% \end{itemize}

\resumeSubHeadingListEnd{}

%-----------------------------------------------

\section{Work Experience}

\resumeSubHeadingListStart{}

\workSubheading{University of Virginia}{Charlottesville, VA}
{Undergraduate Teaching Assistant}{Fall 2018--Current}
{Teaching Assistant for CS 2102 (Discrete Mathematics). Helped students in office hours, suggested improvements to the course, and graded assignments.}

\workSubheading{Impact Makers Inc.}{Richmond, VA}
{Junior Security Associate}{Summer 2018}
{Produced internal IT security documentation and policies for the company intranet hosted on Azure. Took on additional roles including refactoring and setting up an automated build and test pipeline for an internal AWS web application and improving the Impact Makers WordPress website.}

\workSubheading{Impact Makers Inc.}{Richmond, VA}
{Intern}{Summer 2017}
{Worked with the IM Connect team to set up an automated testing framework for a React web app using Nightmare.js, Mocha.js, and Gulp. Gained valuable experience in Agile, Scrum, and continuous integration (CI).}

\workSubheading{Maggie L. Walker Governor's School Mentorship Program}{Richmond, VA}
{Mentee}{2016--2017}
{Worked with a University of Richmond computer science professor to build an iOS app using Swift and the React Native framework.}

%% \workSubheading{DriveFactor Inc.}{Glen Allen, VA}
%% {Intern}{Summer 2014}
%% {Built a web application using Python, JavaScript, HTML, and SQL which meaningfully displayed telematics data hosted on AWS.}

\resumeSubHeadingListEnd{}

%-----------------------------------------------

\section{Skills}

\resumeSubHeadingListStart{}

\skillEntry{Programming Languages}
{Python\ \ $\cdotp$\ \ JavaScript (Node.js)\ \ $\cdotp$\ \ C++\ \ $\cdotp$\ \ Java\ \ $\cdotp$\ \ Emacs Lisp}

\skillEntry{Development \\Technologies}
{Git\ \ $\cdotp$\ \ Shell scripting\ \ $\cdotp$\ \ React Native\ \ $\cdotp$\ \ Linux/Unix\ \ $\cdotp$\ \ Vim/Emacs}

\skillEntry{Languages}
{English\ \ $\cdotp$\ \ Spanish\ \ $\cdotp$\ \ Hindi\ \ $\cdotp$\ \ Japanese\ \ $\cdotp$\ \ Urdu}

\resumeSubHeadingListEnd{}

%-----------------------------------------------

\section{Projects}

\resumeSubHeadingListStart{}

\workSubheading{TriTag}{React Native (JavaScript)\ $\cdotp$\ Arduino (C)}
{https://devpost.com/software/tritag}{MedHacks (September 2018)}
{\textbf{Top Ten in Category}\\ A modern, digital approach to Triage involving an iPad app and an Arduino-based model identifier.}

\workSubheading{Reddit Short Story to PDF}{Python\ $\cdotp$\ \LaTeX}
{https://devpost.com/software/reddit-short-story-to-pdf}{MLH Local Hack Day (December 2017)}
{\textbf{Best Overall Award}\\ A command line utility that gets the top responses from the r/WritingPrompts subreddit and downloads them as a PDF.}

\workSubheading{Astronomy Picture of the Day CLI}{Node.js\ $\cdotp$\ Python\ $\cdotp$\ \LaTeX}
{https://github.com/samarthkishor/astronomy-picture-of-the-day-cli}{}
{A program that scrapes NASA's Astronomy Picture of the Day website and automatically creates a pdf with the picture and explanation.}

\resumeSubHeadingListEnd{}

%-----------------------------------------------

% \vspace{-1.5em}
% \section{Community Service}

% \resumeSubHeadingListStart

% \workSubheading{Music Orchard}{Richmond, VA}
% {Mentor}{2013--2017}
% {Provided pro bono private saxophone lessons to elementary school children.}

% \workSubheading{Sacred Heart Center}{Richmond, VA}
% {Volunteer}{2016}
% {Entered attendance records into a database, called students in Spanish, and helped Spanish-speaking adults with GED preparation in the computer lab.}

% \resumeSubHeadingListEnd

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
